%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{multicol}
\usepackage{ragged2e}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\setlength{\footskip}{4.08003pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\headheight}{0pt}
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\education}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small#4} \\
      \textit{\small#5} \textit{\small#6}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\projecttitle}[2]{
  \noindent
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{\small#1} & \small#2
  \end{tabular*}
  \vspace{-15pt}
}

\newcommand{\techstack}[2]{
  \begin{tabularx}{\textwidth}{l@{\hspace{5pt}} X}
    \textbf{\small#1} & \small#2
  \end{tabularx}
  \vspace{-18pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
  {\Huge \scshape Yashaswini Yellapu} \\ \vspace{1pt}
  \textit{\small (She/her)} \\
  Konigsberger Strasse 33, Furth, 90766 \\ \vspace{1pt}
  \small \href{tel:+49 15221348983}{\raisebox{-0.1\height}\faPhone\ \underline{{+49 15221348983}}} ~
  \href{mailto:yashaswiniyellapu@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{yashaswiniyellapu@gmail.com}} ~
  \href{https://www.linkedin.com/in/yashaswini-y-200500149/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/yashaswini}}  ~
  \href{https://github.com/yashaswiniyellapu}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/yashaswiniyellapu}}
  \vspace{-8pt}
\end{center}

%------ABOUT----------
\section{About}
\begin{justify}
  \resumeSubHeadingListStart
  \resumeItem{Currently pursuing a Master of Science in Autonomy Technologies at FAU Erlangen-Nuremberg, with a strong focus on Signal Processing, Medical Robotics, and Automation. With over two years of experience in software development, I am actively seeking a Working Student position to gain practical industry experience and apply my academic knowledge in real-world projects. My goal is to contribute to innovative solutions while further enhancing my technical and professional skills.}
  \resumeSubHeadingListEnd
\end{justify}

\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\education
{FAU Erlangen-Nuremberg}{April 2024 -- current}
{Master of Science in Autonomy Technologies}{Erlangen, Bayern, Germany}
{Major:} {Signal Processing, Robotics and Automation}
\resumeSubheading
{JNTUA College of Engineering, Pulivendula}{July 2017 -- June 2021}
{Bachelor of Technology in Mechanical Engineering}{Pulivendula, Andhra Pradesh, India}
\resumeSubHeadingListEnd

%------RELEVANT COURSEWORK-------
\section{Areas of Interest}
%\resumeSubHeadingListStart
\begin{multicols}{3}
  \begin{itemize}[itemsep=-5pt, parsep=3pt]
    \item\small Robotics
    \item Autonomous Driving
    \item Computer Vision
    \item Low Code Development
    \item DevOps and CI/CD Integration
    \item Signal Processing
    \item Backend Development
    \item Radar,RFID and Wireless Systems
    \item Image and Video Compression(Image and Video Coding)
  \end{itemize}
\end{multicols}
\vspace*{2.0\multicolsep}
%\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}

\resumeSubHeadingListStart
\resumeSubheading{Everest Engineering}{Aug 2021 - Jan 2024}{Software CraftsPerson}{Bangalore, India}

\projecttitle{Timesheets | Employee Work Hours Tracking}{July 2023 – Jan 2024}

\techstack{Tech Stack:}{TypeScript, SQL, Node.js, React-JS, AWS, GitHub}
\resumeItemListStart
\resumeItem{Achieved a 50\% improvement in overall system performance compared to previous iterations.}
\resumeItem{Enhanced CI/CD processes by streamlining scheduled script execution, leveraging GitHub Actions, resulting in a 25\% increase in automation efficiency.}
\resumeItem{Developed and launched new user-friendly features within an admin interface.}
\resumeItem{Implemented constraints for recording work hours, ensuring a 15\% improvement in data accuracy and compliance.}
\resumeItem{Increased test coverage through the implementation of comprehensive unit tests, enhancing code reliability and quality.}
\resumeItemListEnd


\projecttitle{SeekMaxConnect | Job Portal Mobile Application}{Aug 2022 - June 2023}

\techstack{Tech Stack:}{Node.js, TypeScript, JavaScript, Koa.js, NodeBB, Docker, Buildkite, AWS, MongoDB, Jest, Nock, Datadog, Splunk, PagerDuty, GitHub}
\resumeItemListStart
\resumeItem{Designed and developed multiple APIs with GraphQL and AWS integration.}
\resumeItem{Built an integrated platform, improving user experience by 15\%.}
\resumeItem{Managed on-call support, reducing incident resolution time by 30\%.}
\resumeItem{Led the delivery of the MyThread feature, ensuring seamless integration.}
\resumeItem{Developed Datadog dashboards for API and AWS monitoring, with proficiency in Splunk.}
\resumeItem{Improved test coverage by 35\% with unit and integration tests, enhancing reliability.}
\resumeItemListEnd

\resumeSubheading
{Everest Engineering}{April 2021 -- August 2022}
{Full Stack Developer Intern}{Bangalore, India}

\projecttitle{Employee Portal | Web Application}{}

\techstack{Tech stack:}{Java, SQL, Spring boot}
\resumeItemListStart
\resumeItem{Developed a Java-backed application with a React JS frontend, incorporating CI/CD via GitHub Actions, and deployed it using AWS ECS cloud services.}
\resumeItemListEnd

\projecttitle{Airlines Booking System | Backend Application}{}

\techstack{Tech stack:}{Java, Docker, MySQL, AWS, React}

\resumeItemListStart
\resumeItem{Developed a application for flight ticket booking across Economy, First, and Business classes, utilizing dynamic pricing strategies based on booking dates.}
\resumeItemListEnd

\projecttitle{Parking Lot System | Backend Application}{}

\techstack{Tech stack:}{Java}

\resumeItemListStart
\resumeItem{Created a application to manage parking lots with configurable floors and slots, supporting cars, bikes, and trucks.}
\resumeItem{The system issues parking tickets upon entry and manages vehicle exits based on ticket validation.}
\resumeItemListEnd


\resumeSubHeadingListEnd
\vspace{-16pt}

%----!!!!YASHU FILL THIS--------
%-----------PROJECTS-----------
\section{Projects}

\projecttitle{Automatic Domestic Fire Suppression System}{April 2021 -- June 2021}

\techstack{Tech Stack:}{Arduino, Flame Sensor, GSM Module, Relay Module}

\resumeItemListStart
\resumeItem{Developed a domestic fire safety system that detects, mitigates, and prevents fire accidents using sensors and automation, ensuring enhanced household security.}
\resumeItemListEnd

\projecttitle{Smart Dustbin}{April 2020 -- August 2020}

\techstack{Tech Stack:}{Arduino, Servo Motor, Ultrasonic Sensor}

\resumeItemListStart
\resumeItem{Created a touchless smart dustbin that uses ultrasonic sensors to detect user proximity, automatically opening the lid to improve hygiene and user convenience.}
\resumeItemListEnd

\vspace{-10pt}



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
        \textbf{Languages}{: C, Python, Java, Latex, TypeScript} \\
        \textbf{Databases}{: MySQL, PostgreSQL, MongoDB} \\
        \textbf{Image Processing Libraries}{: OpenCV, NumPy} \\
        \textbf{Developer Tools}{: VS Code, Intellij, Google Cloud Platform, Amazon Web Services} \\
        \textbf{DevOps tools}{: Docker, CI/CD, GitHub, GitLab, BitBucket} \\
        \textbf{Operating Systems}{: Mac, Windows, Linux} \\
        \textbf{Technologies/Frameworks}{: React, Spring-boot, Node.js, JUnit} \\
        \textbf{Soft Skills}{: Time Management, Leadership, Adaptability and Flexibility, Decision Making} \\
        }}
\end{itemize}
\vspace{-16pt}

\section{Certifications}
\resumeItemListStart
\resumeItem{Essentials for NX Designers from \textbf{Siemens}}
\resumeItem{Introduction to Industry 4.0 and Industrial Internet of things from NPTEL}
\resumeItemListEnd
\vspace{-16pt}


\section{Language Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
        \textbf{Mother Tongue}{: Telugu} \\
        \textbf{Other Languages}{: English - B2, German - A1} \\
        }}
\end{itemize}
\vspace{-16pt}


%-----------INVOLVEMENT---------------
\section{Leadership / Extracurricular}
\resumeSubHeadingListStart
\resumeSubheading{Training and Placements Cell }{April 2021}{Coordinator}{JNTUA College of Engineering, Pulivendula}
\resumeItemListStart
\resumeItem{Organized placements activities throughout 2021.}
\resumeItem{Managed the placement data for 60 students.}
\resumeItemListEnd

\resumeSubheading{Robogyan Club Events}{August 2020}{Event Coordinator}{JNTUA College of Engineering, Pulivendula}
\resumeItemListStart
\resumeItem{Organized a workshop on Image processing using Raspberry Pi.}
\resumeItem{Hosted and managed a two-day event for 50 delegates.}
\resumeItemListEnd
\resumeSubHeadingListEnd


\end{document}
