%-------------------------
% Entry-level Cover-letter Template in LaTeX
% Made to go with "Entry-level Resume in laTeX" - here
% Version - v1.0
% Last Edits - October 5, 2021
% Author : Jayesh Sanwal
% Reach out to me on LinkedIn(/in/jsanwal), with any suggestions, ideas, issues, etc.
%------------------------


%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  STARTING HERE, DO NOT TOUCH ANYTHING 
%%%%%%% --------------------------------------------------------------------------------------

%%%% Define Document type
\documentclass[11pt,a4]{article}

%%%% Include Packages
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
 \usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{hyperref}
\usepackage{csquotes}
\usepackage{tabularx}
\hypersetup{colorlinks=true,urlcolor=black}
\usepackage[11pt]{moresize}
\usepackage{setspace}
\usepackage{fontspec}
\usepackage[inline]{enumitem}
\usepackage{ragged2e}
\usepackage{anyfontsize}

%%%% Set Margins
\usepackage[margin=1cm]{geometry}

%%%% Set Fonts
\setmainfont[
path=fonts/,
BoldFont=SourceSansPro-Semibold.otf,
ItalicFont=SourceSansPro-RegularIt.otf
]{SourceSansPro-Regular.otf}

%%%% Set Page Style
\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

%%%% Set URL Style
\urlstyle{same}

%%%% Set Indentation
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%%%% Set Secondary Color, Page Number Color, Footer Text
\definecolor{UI_blue}{RGB}{32, 64, 151}
\definecolor{HF_color}{RGB}{179, 179, 179}
\rfoot{{\color{HF_color} \thepage \ of \ 1, Updated \today}}

%%%% Set Heading Format
\titleformat{\section}{
\color{UI_blue} \scshape \raggedright \large 
}{}{0em}{}[\vspace{-0.7cm} \hrulefill \vspace{-0.2cm}]
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  END OF "DO NOT TOUCH" REGION
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%% --------------------------------------------------------------------------------------



\begin{document}
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  HEADER
%%%%%%% --------------------------------------------------------------------------------------
\begin{center}
    \begin{minipage}[b]{0.24\textwidth}
            \large +49 15207091018 \\
            \large \href{mailto:g.m.venkateshmuni@gmail.com}{g.m.venkateshmuni@gmail.com} 
    \end{minipage}% 
    \begin{minipage}[b]{0.5\textwidth}
            \centering
            {\Huge Muni Venkatesh Ganji} \\ %
            \vspace{0.1cm}
            {\color{UI_blue} \Large{Target Job}} \\
    \end{minipage}% 
    \begin{minipage}[b]{0.24\textwidth}
            \flushright \large
            {\href{https://www.linkedin.com/in/muni-venkatesh-ganji/}{linkedin.com/in/muni} } 
    \end{minipage}   
    
\vspace{-0.15cm} 
{\color{UI_blue} \hrulefill}
\end{center}

\justify
\setlength{\parindent}{0pt}
\setlength{\parskip}{12pt}
\vspace{0.2cm}
\begin{center}
    {\color{UI_blue} \Large{COVER LETTER}}
\end{center}


%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  First 2 Lines
%%%%%%% --------------------------------------------------------------------------------------

Date: \today \par \vspace{-0.1cm}
Dear Hiring Manager, % OR To whom this may concern, 

\par I am writing to express my interest in the working student role at SAAB. With a strong technical background and a passion for networking and connectivity, I am eager to contribute to your innovative projects and gain hands-on experience in Signal Processing and Wireless Communications.

\par During my academic career, I dedicated significant efforts to a graduation project titled "Simulation and Analysis of Spectrum Sensing in Cognitive Radio." This project aimed to address the increasing demand for future bandwidth by exploring the potential of cognitive radio systems. I focused on identifying and utilizing unoccupied spectrum bands within Digital Television channels (DTV) to expand wireless broadband connectivity. To achieve this, I employed energy detection techniques, specifically the double threshold energy detection method, which offers greater accuracy than the existing single threshold detection approach. Through extensive simulations and analysis using MATLAB/Simulink, I could demonstrate this method's effectiveness.

\par After graduating, I began my professional journey as a full-time software engineer at Everest Engineering. Joining as a full-time employee in August 2021, I gained extensive exposure to a diverse range of technologies, ultimately refining my skills in programming and data structures. My tenure at Everest Engineering provided me with valuable hands-on experience in a diverse range of technologies like Android Development and Flutter, allowing me to actively contribute to a variety of production projects for clients worldwide.

\par This project and experience have equipped me with a robust understanding of signal processing, network design, and software development, all of which are crucial for the role at SAAB. I am particularly excited about the opportunity to work on advanced signal processing and communication solutions, which align with my academic interests and professional aspirations. I am eager to apply my knowledge in a practical setting, collaborate with experienced professionals at SAAB, and contribute to groundbreaking projects that push the boundaries of wireless communications and signal processing.

\par Thank you for considering my application. I eagerly anticipate the opportunity to discuss how my background, skills, and aspirations align with the objectives of SAAB.

%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  SIGNATURE
%%%%%%% --------------------------------------------------------------------------------------

\vspace{0.5cm}
\raggedright
Yours Faithfully \\ Muni Venkatesh Ganji \\ +49 15207091018 \\ \href{mailto:g.m.venkateshmuni@gmail.com}{g.m.venkateshmuni@gmail.com}

\end{document}